Total CD4 Data

### 2019-06-17 ICS_CD4.Rmd
LTBI/TB only

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4a<-read.csv("ICS_CD4_clean.csv")
cd4b<-read.csv("ICS_CD4_new.csv")
```

#Are HC and LTBI different or can we combine?
```{r, fig.height=3, fig.width=6}
library(knitr)
colnames<-names(dplyr::select(cd4a, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4a, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

```{r}
colnames<-names(dplyr::select(cd4b, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4b, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

##Test and Return Significant Differences
This will run through each column, and test the relevant comparisons for statistical significance. It also corrects when multiple comparisons are made. Since Healthy Controls are only compared internally, they do not get included in the multiple testing comparison. The function only returns the comparisons that have an initial p-value less than 0.05, which reduces clutter. Everything else is insignificant.
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(cd4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

@@

####Option 1
```{r, fig.width=8, fig.height=8}
data<-filter(cd4, cd4$Stim=="UN", cd4$TB=="HC")
a<-plot_hc(data, "SM", "CXCR3")+labs(title="Surface Marker Expression", subtitle="TH1")
b<-plot_hc(data, "SM", "CCR4")+labs(title=" ", subtitle="TH2")
c<-plot_hc(data, "SM", "Tbet")+labs(title="Transcription Factor Expression", subtitle="TH1")
d<-plot_hc(data, "SM", "GATA3")+labs(title=" ",subtitle="TH2")
plot_grid(a,b,c,d, ncol=2)
```

####Option 2
```{r, fig.width=8, fig.height=8}
a<-plot_hc(data, "SM", "CXCR3")+labs(title="TH1", subtitle="Surface Marker")
b<-plot_hc(data, "SM", "Tbet")+labs(title=" ", subtitle="Transcription Factor")
c<-plot_hc(data, "SM", "CCR4")+labs(title="TH2", subtitle="Surface Marker")
d<-plot_hc(data, "SM", "GATA3")+labs(title=" ", subtitle="Transcription Factor")
plot_grid(a,b,c,d, ncol=2 )
```

>>>>

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4<-read.csv("ICS_CD4_clean.csv")
```

##Test and Return Significant Differences
This will run through each column, and test the relevant comparisons for statistical significance. It also corrects when multiple comparisons are made. Since Healthy Controls are only compared internally, they do not get included in the multiple testing comparison. The function only returns the comparisons that have an initial p-value less than 0.05, which reduces clutter. Everything else is insignificant.
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(cd4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

@@

##Significant on Total CD4+ T cells
```{r, fig.width=12, fig.height=8}
data<-mutate_TB(filter(cd4, cd4$Stim=="UN"))
a<-plot_2(data, "disease", "CCR4")
b<-plot_2(data, "disease", "t_g_x_4")
c<-plot_2(data, "disease", "GATA3")
d<-plot_2(data, "disease", "GATA3.P_Tbet.N")
plot_grid(a,b,c,d, ncol=2)
```

##These are significant amongst Peptide-Specific CD4+ T cells
```{r}
b<-plot_2(data, "disease", "Tbet")+labs(y="Tbet+ Total CD4+ T cells (%)")
c<-plot_2(data, "disease", "t_x_x_4")+labs(y="CCR4+Tbet+ Total CD4+ T cells (%)")
d<-plot_2(data, "disease", "GATA3")+labs(y="GATA3+ Total CD4+ T cells (%)")
plot_grid(b,c,d, ncol=3)
```
